---
title: "run_analysis"
author: "OP"
date: "27/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Explanations

This is sample code for generating a dataframe based on:
[Details](http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones) 
The source dataset can be downloaded from:
[Archive Dataset](https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip)  
It should be extracted from the ZIP file in the same folder than the run_analysis.R code
and keep the same folder structure than stored in the ZIP file.

This code creates a dataframe that contains both test and training data, only for the variables
that represent mean or std values
It also creates a summary dataframe with the means of all of these variables, per subject and per activity

Note that dplyr and data.table packages must be installed.

Here is the sample code to execute:


```{r echo=FALSE, results=''}
source("run_analysis.R")
initializeLibs()
sampleDF <- createARDF() # creates the main Dataframe
tidyDF <- createTidyDF(sampleDF) # creates the tidy Dataframe
library(knitr)
kable(head(sampleDF), format = "simple", caption = "Full dataframe")
kable(head(tidyDF), format = "simple", caption = "Tidy dataframe: Mean per suject and activity")
```

